### 2020-05-27 system-model.tex
:construction: Waveform optimization

		with $z$ given by \ref{eq:z_gp}. We introduce an auxiliary variable $t'$ and transform problem \ref{op:su_gp} into

@@

				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,t'}{\frac{1}{t'}}{\label{op:su_gp_1}}{}

@@

				\addConstraint{\frac{t'}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}

@@

			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t'}{\frac{1}{t'}}{\label{op:su_gp_2}}{}

@@

			\addConstraint{{t'}\prod_m{\left(\frac{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m}}\right)^{-\gamma_{P,m}}}\le{1}}

@@

	\begin{subsection}{Frequency-Flat IRS}
		In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
		\begin{equation}
			\begin{split}
				\lvert{h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}}\rvert^2
				&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{v}_n^H\boldsymbol{\phi}+\boldsymbol{\phi}^H\boldsymbol{v}_n{h_{D,n}}+\boldsymbol{\phi}^H\boldsymbol{v}\boldsymbol{v}^H\boldsymbol{\phi}\\
				&=\bar{\boldsymbol{\phi}}^H\boldsymbol{R}_n\bar{\boldsymbol{\phi}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})
			\end{split}
		\end{equation}
		where $t$ is an auxiliary variable with unit modulus and
		\begin{equation}
			\boldsymbol{R}_n=
			\begin{bmatrix}
				\boldsymbol{v}_n\boldsymbol{v}_n^H & \boldsymbol{v}_n{h_{D,n}} \\
				h_{D,n}^*{\boldsymbol{v}_n^H}      & h_{D,n}^*{h_{D,n}}
			\end{bmatrix},
			\quad \bar{\boldsymbol{\phi}}=\
			\begin{bmatrix}
				\boldsymbol{\phi} \\
				t
			\end{bmatrix},
			\quad \boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H
		\end{equation}
		with $\boldsymbol{R}_n,\boldsymbol{\Phi} \in \mathbb{C}^{(L+1) \times (L+1)}$ and $\bar{\boldsymbol{\phi}} \in \mathbb{C}^{(L+1) \times 1}$. On top of this, the outer product of composite channel rewrites as
		\begin{equation}
			\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{R}^H\boldsymbol{\Phi}\boldsymbol{R}
		\end{equation}
		where $\boldsymbol{R}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$. Hence, the output current \ref{eq:z_k_channel} can be reformulated as $z(\boldsymbol{\Phi})$ (details given in section \ref{se:fs_irs}). To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.

@@

			The phase optimization subproblem is formed as follows. With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, problem \ref{op:su} reduces to
				{\boldsymbol{\boldsymbol{\Phi}}}{z(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
			Introduce auxiliary variables

@@

					&=\mathrm{Tr}(\boldsymbol{R}^H\boldsymbol{\Phi}\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*)\\
					&=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*\boldsymbol{R}^H\boldsymbol{\Phi})\\

@@

			where we define $\boldsymbol{C}_{I/P,n}=\boldsymbol{R}\boldsymbol{W}_{I/P,n}^*\boldsymbol{R}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as

@@

					& \quad + \mathrm{Tr}(t_{I/P,n}^{(i-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{\Phi}^{(i)})\\

@@

					& - \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(i-1)} (t_{I,n}^{(i-1)})^* + t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \\
					& - \frac{3}{2} \beta_4 \rho^2 t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}

@@

			We then plug \ref{eq:z_irs_approx} into problem \ref{op:su_irs}, relax the rank constraint \ref{co:irs_rank}, and obtain the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ by interior-point method. If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD). Otherwise, a best feasible candidate $\bar{\boldsymbol{\phi}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}. First, perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$. Then, generate $R$ CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ r=1,\dots,R$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_r=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$. Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one achieving maximum objective value \ref{eq:su_irs_target}. Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star)$. The algorithm for the phase optimization subproblem is summarized in Algorithm \ref{al:ff_irs}.

@@

					\State Generate CSCG random vectors $\boldsymbol{r}_r \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall r$
					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_r=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_r$ and corresponding matrices $\boldsymbol{\Phi}_r=\bar{\boldsymbol{\phi}}_r\bar{\boldsymbol{\phi}}_r^H  \ \forall r$

@@

			The waveform optimization subproblem is formed as follows. Once $\boldsymbol{\Phi}$ is obtained, problem \ref{op:su} is reduced to
			\begin{maxi}
				{\boldsymbol{W}_I,\boldsymbol{W}_P,\rho}{z(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)}{\label{op:su_waveform}}{}
				\addConstraint{\sum_{n}{\log_2\left(1+\frac{(1-\rho){W}_{I,n,n}\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)} \ge \bar{R}}
				\addConstraint{\frac{1}{2}(\mathrm{Tr}(\boldsymbol{W}_I)+\mathrm{Tr}(\boldsymbol{W}_P))\le{P}}
				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}
				\addConstraint{\mathrm{rank}(\boldsymbol{W}_{I/P})=1}
			\end{maxi}
			Similarly, define $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T$ and let $\boldsymbol{M}_n$ keep the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and null the remaining entries. Since $\boldsymbol{M} \succ 0$, we have $\boldsymbol{M}_{-n}=\boldsymbol{M}_n^H$. Hence, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_waveform}.
				\begin{equation}\label{eq:z_k_waveform}

@@

						z
						&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
						&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{w}_I^H\boldsymbol{M}_{n}\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{M}_{n}\boldsymbol{w}_I)^*+(\boldsymbol{w}_P^H\boldsymbol{M}_{n}\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{M}_{n}\boldsymbol{w}_P)^*}\\
						&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_{0}\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_{0}\boldsymbol{w}_P)}

@@

			Introduce auxiliary variables
					t'_{I/P,n}
					& = \boldsymbol{w}_{I/P}^H\boldsymbol{M}_{n}\boldsymbol{w}_{I/P}\\
					& = \mathrm{Tr}(\boldsymbol{M}_{n}\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H)\\
					& = \mathrm{Tr}(\boldsymbol{M}_{n}\boldsymbol{W}_{I/P})
			where $\boldsymbol{W}_{I/P}=\boldsymbol{w}_{I/P}\boldsymbol{w}_{I/P}^H$. Therefore, \ref{eq:z_k_waveform} rewrites as
			\begin{equation}\label{eq:z_k_waveform_t}
					z
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t'_{I,0}+t'_{P,0})\\
					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t'_{I,0}t'_{P,0}
			At iteration $k$, the second-order terms are approximated by first-order Taylor series as

@@

					t_{I/P,n}^{\prime \ (k)} (t_{I/P,n}^{\prime \ (k)})^*
					& \approx 2 \Re\left\{t_{I/P,n}^{\prime \ (k)} (t_{I/P,n}^{\prime (k-1)})^*\right\} - t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^* \\
					& = 2 \Re \left\{\mathrm{Tr}((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(i)})\right\} - t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^*\\
					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n}\boldsymbol{W}_{I/P}^{(i)}\right) + \mathrm{Tr}(t_{I/P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\boldsymbol{W}_{I/P}^{(i)})\\
					& \quad- t_{I/P,n}^{\prime (k-1)} (t_{I/P,n}^{\prime (k-1)})^*

@@

					t_{I,0}^{\prime \ (k)} t_{P,0}^{\prime \ (k)}
					& \approx t_{I,0}^{\prime \ (k)} t_{P,0}^{\prime (k-1)} + t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime \ (k)} - t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}\\
					& = \mathrm{Tr}\left(t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{I,0}^{(i)}\right) + \mathrm{Tr}(t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}\boldsymbol{W}_{P,0}^{(i)}) - t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}

@@

			Therefore, we have

@@

					\tilde{z}(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i-1)})
					& = \mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)}) \\
					& - \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (k-1)} (t_{I,n}^{\prime (k-1)})^* + t_{P,n}^{\prime (k-1)} (t_{P,n}^{\prime (k-1)})^* \\
					& - \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)} t_{P,0}^{\prime (k-1)}

@@

			\begin{equation}\label{eq:A_I,k}

@@

					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{I,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H\right) \\
					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{P,0}^{\prime (k-1)}\boldsymbol{M}_{0}

@@

			\begin{equation}\label{eq:A_P,k}

@@

					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (k-1)})^*\boldsymbol{M}_{n} + t_{P,n}^{\prime (k-1)}\boldsymbol{M}_{n}^H \\
					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (k-1)}\boldsymbol{M}_{0}

>>>>

		with $z$ given by \ref{eq:z_gp}. We introduce an auxiliary variable $t''$ and transform problem \ref{op:su_gp} into

@@

				{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,t''}{\frac{1}{t''}}{\label{op:su_gp_1}}{}

@@

				\addConstraint{\frac{t''}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)} \le 1}

@@

			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho,\bar{\rho},t''}{\frac{1}{t''}}{\label{op:su_gp_2}}{}

@@

			\addConstraint{{t''}\prod_m{\left(\frac{g_{P,m}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m}}\right)^{-\gamma_{P,m}}}\le{1}}

@@

	\begin{subsection}{Frequency-Flat IRS}
		In contrast, frequency-flat IRS reflects all subbands equally with a DoF of $L$. We observe that
		\begin{equation}
			\begin{split}
				\lvert{h_{D,n}+\boldsymbol{v}_n^H\boldsymbol{\phi}}\rvert^2
				&=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{v}_n^H\boldsymbol{\phi}+\boldsymbol{\phi}^H\boldsymbol{v}_n{h_{D,n}}+\boldsymbol{\phi}^H\boldsymbol{v}\boldsymbol{v}^H\boldsymbol{\phi}\\
				&=\bar{\boldsymbol{\phi}}^H\boldsymbol{R}_n\bar{\boldsymbol{\phi}}=\mathrm{Tr}(\boldsymbol{R}_n\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H)=\mathrm{Tr}(\boldsymbol{R}_n\boldsymbol{\Phi})
			\end{split}
		\end{equation}
		where $t$ is an auxiliary variable with unit modulus and
		\begin{equation}
			\boldsymbol{R}_n=
			\begin{bmatrix}
				\boldsymbol{v}_n\boldsymbol{v}_n^H & \boldsymbol{v}_n{h_{D,n}} \\
				h_{D,n}^*{\boldsymbol{v}_n^H}      & h_{D,n}^*{h_{D,n}}
			\end{bmatrix},
			\quad \bar{\boldsymbol{\phi}}=\
			\begin{bmatrix}
				\boldsymbol{\phi} \\
				t
			\end{bmatrix},
			\quad \boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H
		\end{equation}
		with $\boldsymbol{R}_n,\boldsymbol{\Phi} \in \mathbb{C}^{(L+1) \times (L+1)}$ and $\bar{\boldsymbol{\phi}} \in \mathbb{C}^{(L+1) \times 1}$. On top of this, the outer product of composite channel rewrites as
		\begin{equation}
			\boldsymbol{h}\boldsymbol{h}^H=\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}
		\end{equation}
		where $\boldsymbol{M}=[\boldsymbol{V}^H,\boldsymbol{h}_D]^H \in \mathbb{C}^{(L+1) \times N}$. To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that iteratively updates the phase shifts and the waveforms with the other being fixed.

@@

			The phase optimization subproblem is formed as follows. With a given waveform $\boldsymbol{w}_I,\boldsymbol{w}_P,\rho$, introduce auxiliary variables

@@

					&=\mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*)\\
					&=\mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H\boldsymbol{\Phi})\\

@@

			where we define $\boldsymbol{C}_{I/P,n}=\boldsymbol{M}\boldsymbol{W}_{I/P,n}^*\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, \ref{eq:z_k_channel} rewrites as

@@

					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{(i-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{\Phi}^{(i)}\right)\\

@@

					& \quad - \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(i-1)} (t_{I,n}^{(i-1)})^* + t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \\
					& \quad - \frac{3}{2} \beta_4 \rho^2 t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}

@@

			Hence, problem \ref{op:su} is transformed to
				{\boldsymbol{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:su_irs}}{\label{eq:su_irs_target}}
			We then relax the rank constraint \ref{co:irs_rank} and solve the optimal IRS matrix $\boldsymbol{\Phi}^{\star}$ iteratively by interior-point method. If $\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ is attained by eigenvalue decomposition (EVD). Otherwise, a best feasible candidate $\bar{\boldsymbol{\phi}}^\star$ can be extracted through Gaussian randomization method \cite{Huang2010}. First, perform EVD on $\boldsymbol{\Phi}^{\star}$ as $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}^H$. Then, we generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$ and construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$. Next, the optimal solution $\bar{\boldsymbol{\phi}}^\star$ is approximated by the one achieving maximum objective value \ref{eq:su_irs_target}. Finally, we can retrieve the phase shift by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The algorithm for the phase optimization subproblem is summarized in Algorithm \ref{al:ff_irs}.

@@

					\State Generate CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}) \ \forall q$
					\State Construct candidate IRS vectors $\bar{\boldsymbol{\phi}}_q=\boldsymbol{U}_{\boldsymbol{\Phi}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{\Phi}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H  \ \forall q$

@@

			Consider the waveform optimization subproblem. Once $\boldsymbol{\Phi}$ is obtained, introduce auxiliary variables
				t_{I/P,n}' = \boldsymbol{w}_{I/P}^H \boldsymbol{H}_n^* \boldsymbol{w}_{I/P} = \mathrm{Tr}(\boldsymbol{H}_n^*\boldsymbol{W}_{I/P})
			Therefore, \ref{eq:z_k_waveform} rewrites as
			\begin{equation}\label{eq:z_waveform}

@@

					z(\boldsymbol{W}_I,\boldsymbol{W}_P,\rho)
					&=\frac{1}{2} \beta_2 \rho (t'_{I,0}+t'_{P,0})\\
					&\quad+\frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\
					&\quad+\frac{3}{2} \beta_4 \rho^2 t'_{I,0}t'_{P,0}

@@

			At iteration $i$, the second-order terms are approximated by first-order Taylor series as

@@

					t_{I/P,n}^{\prime \ (i)} (t_{I/P,n}^{\prime \ (i)})^*
					& \approx 2 \Re\left\{t_{I/P,n}^{\prime \ (i)} (t_{I/P,n}^{\prime (i-1)})^*\right\} - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^* \\
					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\right\}\\
					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*\\
					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\\
					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{I/P}^{(i)}\right)\\
					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*

@@

					t_{I,0}^{\prime \ (i)} t_{P,0}^{\prime \ (i)}
					& \approx t_{I,0}^{\prime \ (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime \ (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\\
					& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I,0}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P,0}^{(i)})\\
					& \quad - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}

@@

@@

					\tilde{z}(\boldsymbol{W}_I^{(i)},\boldsymbol{W}_P^{(i)},\rho^{(i)})
					& = \mathrm{Tr}(\boldsymbol{A}_I^{(i)}\boldsymbol{W}_I^{(i)}) + \mathrm{Tr}(\boldsymbol{A}_P^{(i)}\boldsymbol{W}_P^{(i)})\\
					& - \frac{3}{8} \beta_4 (\rho^{(i)})^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (i-1)} (t_{I,n}^{\prime (i-1)})^* + t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^* \\
					& - \frac{3}{2} \beta_4 (\rho^{(i)})^2 t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}

@@

			\begin{equation}\label{eq:A_I}

@@

					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{\prime (i-1)})^*\boldsymbol{M}_{n} + t_{I,n}^{\prime (i-1)}\boldsymbol{M}_{n}^H\right) \\
					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{P,0}^{\prime (i-1)}\boldsymbol{M}_{0}

@@

			\begin{equation}\label{eq:A_P}

@@

					& + \frac{3 k_4 (\rho^{(i-1)})^2 R_{\text{ant}}^2}{8} \sum_{n=-N+1}^{N-1} (t_{P,n}^{\prime (i-1)})^*\boldsymbol{M}_{n} + t_{P,n}^{\prime (i-1)}\boldsymbol{M}_{n}^H \\
					& + \frac{3{k_4}{(\rho^{(i-1)})^2}{R_{\text{ant}}^2}}{2} t_{I,0}^{\prime (i-1)}\boldsymbol{M}_{0}
